---
title: "Ecosia reports 2018"
author: "Erik Ländström"
date: "9 April 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document is for playing around with the data I extracted from the 2018 
ecosia reports. I'm missing data for reserves right now, but I will revisit that
in the future (or I can probably calculate it from the other data).

```{r}
library(tidyverse)
```

First, read data.

```{r}
raw_data <- read_tsv("ecosia_2018_reports_data.txt")

raw_data 
```

1. The data in `invest_saved` can be negative, but it didn't get extracted.

2. `reserves` were not extracted for all months, but since I have all other major
data I should be able to calculate it.

3. I'm missing operation costs for February, so I will just add that.

```{r}
# 3 
raw_data[2, 9] <- 208797

data <- raw_data %>% 
  mutate(invest_saved = if_else(invest_tot - invest_tree < 0, -invest_saved, invest_saved), # 1
         reserves     = income - invest_tot - ads - costs) # 2

data
```

Calculate totals for 2018.

```{r}
data_2018 <- data %>% 
  select(year, income:costs, trees) %>% 
  group_by(year) %>% 
  summarise_all(sum)
```

